A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
related work

@@

>>>>

The adult database has been widely used to benchmark novel learning algorithms.

In the article \textit{Scaling Up the Accuracy of Naive-Bayes Classifiers: a Decision Tree hybrid},
the author presents the nbtree algorithm, which is an hybrid approach suitable in learning scenarios
when many attributes are likely to be relevant for a classification task, yet the attributes
are not necessarily conditionally independent given the class \cite{nbtree}. It builds
a decision tree with bayesian classifiers at the leaves.

In the paper the author used various datasets, including the adult database. Records with unknown values
were removed from the experiments. C4.5 reached an error rate of $\approx$15\% and NBTree $\approx$16.5\%,
which are identical to our ID3 results, but worse than our C4.5 experiments. One reason for this is
the incapability of Weka to use numeric attributes. Every other algorithm we used fared worse ($\approx$20\%).

Another paper, \textit{Learning Bayesian Belief Network Classifiers: Algorithms and System}, explores
various kinds of search algorithms used in Bayesian Networks and also comes up with very good error rates ($\approx$ 15\%).
Other papers using this dataset can be found in \cite{dataset_papers}.

The location from where we downloaded the dataset also contains results
using various algorithms (Table \ref{tbl:dataset_error_rates}).

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c |}
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    C4.5 & 15.54 \\ \hline
    C4.5-auto & 14.46 \\ \hline
    C4.5 rules & 14.94 \\ \hline
    Voted ID3 (0.6) & 15.64 \\ \hline
    Voted ID3 (0.8) & 16.47 \\ \hline
    T2 & 16.84 \\ \hline
    1R & 19.54 \\ \hline
    NBTree & 14.10 \\ \hline
    CN2 & 16.00 \\ \hline
    HOODG & 14.82 \\ \hline
    FSS Naive Bayes & 14.05 \\ \hline
    IDTM (Decision table) & 14.05 \\ \hline
    IDTM (Decision table) & 14.46 \\ \hline
    Naive-Bayes & 16.12 \\ \hline
    Nearest-neighbor (1) & 21.42 \\ \hline
    Nearest-neighbor (3) & 20.35 \\ \hline
    OC1 & 15.04 \\ \hline
  \end{tabular}
  \caption{Error rates from the dataset.}
  \label{tbl:dataset_error_rates}
  \end{center}
\end{table}

@@

\bibitem{nbtree}
Ron Kohavi. Scaling Up the Accuracy of Naive-Bayes Classifiers: a Decision-Tree Hybrid. 1996

\bibitem{dataset_papers}
Adult Data Set, Machine Learning Repository, \url{http://archive.ics.uci.edu/ml/datasets/Adult}

\bibitem{bayes4}
Jie Cheng, Russell Greiner. Learning Bayesian Belief Network Classifiers: Algorithms and System. 2001
